\mytitile\\~

### 2019-11-03 document.tex
Proofread a bit

The manuscript consists of four main parts and an Appendix. Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research; finally, in Section IV we make a conclusion of our work and discuss future prospects. The Appendix contains important details of the theoretical framework that we use to model the observed processes.

@@

\subsection{Device design and fabrication}
We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which serves both to couple\cite{majer2007coupling} the qubits and for the joint\cite{chow2010detecting} readout of their states. In \autoref{fig:experiment}~(a) the optical photograph of the device is shown depicting the layout of the components. The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed. In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler. Flux lines that allow independent control of the $ge$ transitions of the transmons are coming from the sides. Finally, the excitation waveguide coming from below directs microwave signal towards the SAM. In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device. The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances. The capacitively coupled excitation line is also shown in green. Finally, in \autoref{fig:experiment}~(c) we show schematically the $ge$ transitions of the transmons depending on the external magnetic flux. Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue). Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)). This is convenient as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are staying close to each other in frequency. Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.

@@

A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$ ($\hbar = 1$):
\begin{equation}
\hat{{H}}_{tr} = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\end{equation}
where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the  $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon. Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}. In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

>>>>

The manuscript consists of four main parts and an Appendix. Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research; finally, in Section IV we make a conclusion of our work and discuss future prospects. The Appendix contains important details of the theoretical framework that we use.

@@

\subsection{Device design and fabrication}
We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the qubits and allows the joint\cite{chow2010detecting} readout of their states. In \autoref{fig:experiment}~(a), the optical photograph of the device is shown depicting the layout of the components. The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed. In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler. Flux lines that allow independent control of the transmon frequencies are coming from the sides. Finally, the excitation waveguide coming from below directs microwave signal towards the SAM. In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device. The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances. The capacitively coupled excitation line is also shown in green. Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux. Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue). Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)). This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are staying close to each other in frequency. Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.

@@

A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$ ($\hbar = 1$):
\begin{equation}
\hat{{H}}_{tr} = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\end{equation}
where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the  $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon. Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}. In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).
